---
title: "Appendix B Further statistical analyses"
subtitle: "Reproduce efforts"
output: html_document
---

```{r setup, include=FALSE}
# libraries ----
library(dplyr)
library(readxl)
library(ggplot2)
library(kableExtra)
library(pscl)
# options ----
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# functions ----
#' Perform Mann-Whitney U test
#'
#' @param df_ data.frame
#' @param group_column_name name of column with groups
#' @param group_1_name name of first group
#' @param group_2_name name of second group
#' @param value_name name of column with values to compare
#'
#' @return
#' @export
#'
#' @examples
#' do_mann_whitney(mtcars, "cyl", "4", "6", "mpg")
do_mann_whitney <- function(df_, group_column_name, group_1_name, group_2_name, value_name) {
    y1 <- df_[df_[[group_column_name]] == group_1_name, ][[value_name]]
    y2 <- df_[df_[[group_column_name]] == group_2_name, ][[value_name]]
    wilcox.test(y1, y2)
}

#' Prettify data.frame with coeffecients
#'
#' @param x data.frame with coeefficients
#'
#' @return
#' @export
#'
#' @examples
#' pretty_t(summary(lm(hp ~ ., mtcars))$coefficients, pvalue_name = "Pr(>|t|)")
pretty_t <- function(x, pvalue_name = "Pr(>|z|)") {
    zero_model <- as.data.frame(x)
    # Getting variable names
    zero_model$vars <- row.names(zero_model)
    # Removing intercept
    zero_model <- zero_model[zero_model$vars != "(Intercept)", ]
    # Copying column with pvalue
    zero_model$pvalue <- zero_model[[pvalue_name]]
    # Creating print-friendly column
    zero_model <- zero_model %>% 
        mutate(rounded_est = round(Estimate, 3),
               rounded_std = round(`Std. Error`, 3),
               rounded_pvl = round(pvalue, 3),
               to_print = paste0(rounded_est,"<br>(", rounded_std, ")[", rounded_pvl, "]"))
    # Removing redundant columns and row.names 
    zero_model <- zero_model[c("vars", "to_print")]
    row.names(zero_model) <- NULL
    zero_model
}

#' Merge list of data.frames
#'
#' @param df_list_to_merge list of data frames to merge
#' @param merge_by name of column to merge by
#'
#' @return
#' @export
#'
#' @examples
#' to_frame_multi(list(data.frame(var1 = c("A", "V"), var2 = 3:4), data.frame(var1 = c("V", "W"), var2 = 1:2)), "var1")
to_frame_multi <- function(df_list_to_merge, merge_by = "vars") {
    Reduce(function(x, y) merge(x, y, by = merge_by, all = T, sort = F), x = df_list_to_merge)
}

# reading data ----
link_to_data <- "https://osf.io/download/uh4z7/?view_only=de730bd958ef4711819216d30361c8d8"
file_to_save <- "data_DMDDG.xls"

if (!file.exists(file_to_save)) download.file(url = link_to_data, destfile = file_to_save)

df_ <- read_xls(file_to_save)

# data manipulation ----
df_$treatment_group <- ifelse(grepl("^control", df_$treatment), "C",
                              ifelse(grepl("^delay", df_$treatment), "TD", "MD"))

df_$game_type <- ifelse(df_$bully == 0, "SDG", "BDG")
df_$game_type <- factor(df_$game_type, levels = c("SDG", "BDG"))
df_$bully_type <- ifelse(df_$bully == 0, "NB", "B")
df_$give <- 60 - df_$kept
```

## B.2 Multiple hypothesis adjustments

```{r mult_hyp_adj}
# pvalues used by authors
authors_p_values <- c(0.7654, 0.4206, 0.2735, 0.7723, 0.0136, 0.0078, 0.2025, 0.1997, 0.0095)
# pvalues reported as adjusted by authors using Benjamini Hochberg 95 method
reported_adjusted_reported_p_values <- c(0.7723, 0.5401, 0.4103, 0.7723, 0.0408, 0.0408, 0.3645, 0.3645, 0.0408)
# pvalues adjusted using Benjamini Hochberg 95 method based on pvalues provided by authors
adjusted_reported_values <- p.adjust(authors_p_values, method = "BH")

# our pvalues
our_pvalues <- list(
    `(NB) C vs TD` = do_mann_whitney(df_ %>% filter(bully_type == "NB"), "treatment_group", "C", "TD", "kept")$p.value,
    `(NB) TD vs MD` = do_mann_whitney(df_ %>% filter(bully_type == "NB"), "treatment_group", "TD", "MD", "kept")$p.value,
    `(NB) C vs MD` = do_mann_whitney(df_ %>% filter(bully_type == "NB"), "treatment_group", "C", "MD", "kept")$p.value,
    `\\(B) C vs TD` = do_mann_whitney(df_ %>% filter(bully_type == "B"), "treatment_group", "C", "TD", "kept")$p.value,
    `\\(B) TD vs MD` = do_mann_whitney(df_ %>% filter(bully_type == "B"), "treatment_group", "TD", "MD", "kept")$p.value,
    `\\(B) C vs MD` = do_mann_whitney(df_ %>% filter(bully_type == "B"), "treatment_group", "C", "MD", "kept")$p.value,
    `\\(C) NB vs B` = do_mann_whitney(df_ %>% filter(treatment_group == "C"), "bully_type", "B", "NB", "kept")$p.value,
    `(TD) NB vs B` = do_mann_whitney(df_ %>% filter(treatment_group == "TD"), "bully_type", "B", "NB", "kept")$p.value,
    `\\(MD) NB vs B` = do_mann_whitney(df_ %>% filter(treatment_group == "MD"), "bully_type", "B", "NB", "kept")$p.value
)

# our adjusted pvalues
our_adj_pv <- p.adjust(unlist(our_pvalues), method = "BH")

# print the results
kable(x = data.frame(vars = names(our_pvalues),
                     authors_p_values = authors_p_values, 
                     reported_adjusted_reported_p_values = reported_adjusted_reported_p_values, 
                     adjusted_reported_values = round(adjusted_reported_values,4),
                     our_pvalues = round(unlist(our_pvalues), 4),
                     our_adj_pv = round(our_adj_pv, 4), 
                     row.names = NULL), 
      caption = "Control for multiple hypothesis testing using Benjamini and Hochberg (1995)", 
      col.names = c("Dependent variable: Got hypothesis", "(p-value)", "(adjusted)", "(adjusted p-values)", "(our-pvalues)", "(our adj p values)")) %>% 
    kable_styling()
```

Comment: 

- there is a difference between adjusted p-values reported in paper and adjustment based on the reported pvalues for (NB) TD vs MD group (0.5401 vs 0.5408) and (NB) C vs MD group (0.4103 vs 0.4102)
- there is a slight difference in pvalues for Mann-Whitey test reported in paper and based on our calculations. This difference however is small, on the fourth digits, and it does not change the conclusions
- adjusting our p-values yields similar results to adjusted p-values reported in paper.

## B.5 Frequencies of Got by treatment and Hurdle models

The figure illustrates the frequency distribution of the amounts retained by dictators in each condition.

```{r got_hist}
df_ %>% group_by(bully_type, treatment_group, kept) %>% 
    summarise(pp = n()) %>% 
    group_by(bully_type, treatment_group) %>% 
    mutate(nn = sum(pp), pp2 = pp/nn) %>%
    ungroup() %>% 
    ggplot() +
    geom_col(aes(x = kept, y = pp2)) +
    labs(x = "got", y = "Percent") +
    scale_y_continuous(labels = scales::percent) +
    facet_wrap(~bully_type + treatment_group) + theme_minimal()
```

Comment:

- there is slight difference comparing reported histograms to our histogram
- this difference however does not change conclusion regarding need to consider Hurdle model

Reproducing Hurdle Model

```{r hurdle}
# Declaring models
h1 <- hurdle(formula = give ~ game_type + treatment_group + crt_right + as.factor(female) + household_income, data = df_)
h2 <- hurdle(formula = give ~ game_type + treatment_group + crt_right + as.factor(female) + household_income + ee + nb + ne, data = df_)
h3 <- hurdle(formula = give ~ game_type + treatment_group + crt_int + as.factor(female) + household_income, data = df_)
h4 <- hurdle(formula = give ~ game_type + treatment_group + crt_int + as.factor(female) + household_income + ee + nb + ne, data = df_)

# Printing results for count part
kable(x = to_frame_multi(lapply(list(h1, h2, h3, h4), function(x) pretty_t(summary(x)$coefficients$count))), 
      col.names = c("Variable", "right", "right", "intuitive", "intuitive"), caption = "First hurdle", escape = F) %>% 
    kable_styling()
```

```{r}
# Printing results for zero part
kable(x = to_frame_multi(lapply(list(h1, h2, h3, h4), function(x) pretty_t(summary(x)$coefficients$zero))), 
      col.names = c("Variable", "right", "right", "intuitive", "intuitive"), caption = "Second hurdle", escape = F) %>% 
    kable_styling()
```